Rigidity of Expectation: Additional Evidence from Desntify Forecasts

### 2019-06-27 paper/Draft.tex
to finish rest of the drafting.

%opening
\title{Rigidity of Expectation Formation: Additional Evidence from Desntify Forecasts}
\author{Tao Wang}

@@

The second batch of tests in Table \ref{RevEfficiency} focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \citet{nordhaus1987forecasting} and \citet{fuhrer2018intrinsic}. In particular, I follow the model specifications in \citet{fuhrer2018intrinsic}. According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information. For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.  A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.

>>>>

%opening
\title{Rigidity of Expectation: Additional Evidence from Desntify Forecasts}
\author{Tao Wang}

@@

The second batch of tests in Table \ref{RevEfficency} focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \citet{nordhaus1987forecasting} and \citet{fuhrer2018intrinsic}. In particular, I follow the model specifications in \citet{fuhrer2018intrinsic}. According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information. For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.  A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.
